Finalized Plots

### 2022-05-27 Fish Data Analysis/Final_Plots_3D.Rmd
Fixed issue with 3D school NND, 999s didn't leave

```{r}
count_within_2_aligned <- raw_school_data_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
                                                        filter(Heading_Diff > -30 & Heading_Diff < 30) %>%
                                                        group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
                                                        summarise(Count_Fish_in_2BL = sum(Distance <= 2)) %>%
                                                        ungroup() %>%
                                                        group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
                                                        summarise(Mean_Count_Fish_in_2BL = mean(Count_Fish_in_2BL)) %>%
                                                        ungroup()
```

>>>>

```{r}
count_within_2_aligned <- raw_school_data_both_fish %>% mutate(Tailbeat = round_any(Frame_Num, tailbeat_len)/tailbeat_len+1) %>%
                                                        filter(Yaw_Heading_Diff > -30 & Yaw_Heading_Diff < 30) %>%
                                                        group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat, Frame_Num, Fish1) %>%
                                                        summarise(Count_Fish_in_2BL = sum(Distance <= 2)) %>%
                                                        ungroup() %>%
                                                        group_by(Year, Month, Day, Trial, Flow, Ablation, Darkness, Tailbeat) %>%
                                                        summarise(Mean_Count_Fish_in_2BL = mean(Count_Fish_in_2BL)) %>%
                                                        ungroup()
```
